---
title: "Assignment 1"
author: "Marguerite CAMERON"
date: "1 octobre 2017"
output: html_document
---

## Exercise 1

## Exercise 2

```{r}
possible_outcomes <- c(0, 1, 2, 3, 4, 5)
outcome_probabilities <- c(0.1, 0.5, 0.2, 0.1, 0.05, 0.05)
n_data_points <- 400

set.seed(1)
fake_data_points <- sample(possible_outcomes,
                          n_data_points,
                          replace=T,
                          prob=outcome_probabilities)
set.seed(NULL)

fake_data_set <- tibble::data_frame(`Fake measurement`=fake_data_points)
```

```{r}
ggplot2::ggplot(fake_data_set, ggplot2::aes(x=`Fake measurement`)) +
ggplot2::geom_histogram(bins=5, colour="black", fill="lightgrey")
```

Statement 1 (written prior to reading example statements in PDF)

* My understanding is that 400 fake data points have been generated by R according to the parameters outlined in the code.
* The "possible_outcomes" refer to the possible data points that can be generated.  In this case, the possibilities are the whole integers 0-5.
* I assume that the "outcome_probabilities" refers to the respective probabilities of the possible data points.  For example, the possible data point 0 has a probability of 0.1 ; in other words, there is a 10% chance of a data point 0 being generated.
* "n_data_points" specifies the number of data points to be generated. In this case, 400.


## Exercise 3

## Exercise 4

## Exercise 5
