---
title: "Assignment 1"
author: "Marguerite CAMERON"
date: "1 octobre 2017"
output: html_document
---

## Exercise 1

## Exercise 2

```{r}
possible_outcomes <- c(0, 1, 2, 3, 4, 5)
outcome_probabilities <- c(0.1, 0.5, 0.2, 0.1, 0.05, 0.05)
n_data_points <- 400

set.seed(1)
fake_data_points <- sample(possible_outcomes,
                          n_data_points,
                          replace=T,
                          prob=outcome_probabilities)
set.seed(NULL)

fake_data_set <- tibble::data_frame(`Fake measurement`=fake_data_points)
```

```{r}
ggplot2::ggplot(fake_data_set, ggplot2::aes(x=`Fake measurement`)) +
ggplot2::geom_histogram(bins=5, colour="black", fill="lightgrey")
```

Statement 1 (written prior to reading example statements in PDF)

* My understanding is that 400 fake data points have been generated by R according to the parameters outlined in the code.
* The "possible_outcomes" refer to the possible data points that can be generated.  In this case, the possibilities are the whole integers 0-5.
* I assume that the "outcome_probabilities" refers to the respective probabilities of the possible data points.  For example, the possible data point 0 has a probability of 0.1 ; in other words, there is a 10% chance of a data point 0 being generated.
* "n_data_points" specifies the number of data points to be generated. In this case, 400.

Rewriting of Statements, conforming to the convention of writing one "statement" for each separate line of code.  (written after reading example statements in PDF)

Statement 1

* "possible_outcomes" is the name of a numeric variable, and the contents of the variable are the whole integers 0-5.
* The data points generated in the console are, indeed, restricted to occurances of the whole integers 0-5, which confirms that these are the possible outcomes.

Statement 2

* "outcome_probabilities" is a variable for which the contents are the respective distributions of the possible outcomes.  
* Each probability is matched up to an outcome.  For example, the probability of the outcome 1 is 0.5 or 50%. Half of the data points generated can be expected to be 1.

Statement 3

* n_data_points is a variable that determines how many data points will be generated.  In this case, 400.
* To verify, I counted the last line of the data points generated in the Console, up from 377, and got 400.

Statement 4

* I had to look up what the "set.seed" function is.  From what I understand, it has to do with controlling the randomness of the data point generation so that the same data can be "randomly" generated by the same code during different sessions on the same computer, or on a different computer.  

Statement 5

* "fake_data_points" is the variable whose contents are the 400-point sample generated with the above parameters.
* I looked up the meaning of "replace=T".  It is a function that allows the possible outcomes to be sampled more than once.  This is useful for our particular data set, as there are only 6 possible outcomes, but we need to generate 400 data points. 
* sample takes a sample of the specified size from the elements available (in this case the possible_outcomes), either with or without replacement (in this case, with replacement)
* Our sample function chooses elements available from possible_outcomes, 400 of them (n_data_points), allows for replacement (explained above), at the probability weights for the sampled vector (given in outcome_probabilities)

Statement 6

* I looked up what a data frame in R is.  It is used for storing data tables.  It is a list of vectors of equal length.  Tibble is a particular type of data frame, one which allows for more efficient coding.

## Exercise 3

```{r}
iris_groups23 <- dplyr::filter(iris, Species %in% c("versicolor", "virginica"))
ggplot2::ggplot(iris_groups23, ggplot2::aes(x=Sepal.Width)) +
ggplot2::geom_histogram(colour="black", fill="lightgrey", binwidth=0.1) +
ggplot2::facet_grid(Species ~ .)
```

## Exercise 4

## Exercise 5
